Signatures of Foreground Sky in Power Spectra of Redshifted Neutral Hydrogen from the Epoch of Reionization

### 2014-09-03 foreground_delay_spectrum_modeling.tex
more edits in intro

 Matching real observations from the Murchison Widefield Array Epoch of Reionization observing program with instrumental simulations of the entire known sky we are examine the signature of the foreground power spectrum on each baseline.  We discover that the foregrounds most likely to obfuscate the Epoch of Reionization power are not caused by power emitted from the same sky location as the target HI signal, and that smooth galactic emission plays a larger role then previously thought. We quantify this contamination by breaking the simulations down by sky region and type of emission. Using these we arrive at a new method for minimizing the contribution of bright foregrounds which uses prior knowledge of the sky to downweight badly contaminated baselines.

>>>>

 Matching real observations from the Murchison Widefield Array Epoch of Reionization observing program with instrumental simulations of the entire known sky we examine the signature of the power spectrum of each baseline.  We confirm that the foregrounds most likely to obfuscate the Epoch of Reionization power are not caused by emission central field of view but rather from near the horizon. We also find that the smooth galactic emission plays a larger role then previously thought. We quantify this contamination by breaking the simulations down by sky region and type of emission. Using these we arrive at a new method for minimizing the contribution of bright foregrounds which uses prior knowledge of the sky to downweight badly contaminated baselines.
